rmd revealjs Latex test

### 2020-02-07 nontex/revealjsrmd/test_tex.Rmd
rmd math and tex

@@

# Equations New Command

@@

>>>>

<!--
decktape convert to PDF
cd "C:/Users/fan/Tex4Econ/nontex/revealjsrmd/"
decktape automatic test_tex.html test_tex.pdf
-->

@@

# Equations Space Saving

The paper latex file already contains various newcommands pre-defined, want to share those latex files with RMD.

## New Command Define First

Define long newcommand in RMD and show equation multiple times.

@@

## INclude Equations and Symbols Defined Elsewhere

```{r echo=TRUE, eval=FALSE}
{r child = 'test_tex_define.tex'}
```

```{r child = 'test_tex_define.tex'}
```

<span style="font-size:40%;"> $$\exa$$ </span>
<span style="font-size:40%;"> $$\exb$$ </span>
<span style="font-size:40%;"> $$\exc$$ </span>
